Timing and magnitude of climate driven range shifts in transboundary fish stocks challenge their management

### 2021-10-28 Scripts/Manuscript.Rmd
misc.

---
title: "Timing and magnitude of climate driven range shifts in transboundary fish stocks challenge their management"
date: "Affiliations: ^1^Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada.^2^Center for Limnology, University of Wisconsin, Madison. ^3^Climate and Environmental Physics, Physics Institute, University of Bern. ^4^Oeschger Centre for Climate Change Research, University of Bern, Switzerland. ^5^School of Environmental Sciences, University of Liverpool. ^6^Stanford Center for Ocean Solutions, Stanford University, Stanford, United States"
subtitle: "Juliano Palacios-Abrantes*^1,2^, Thomas L. Frölicher^3,4^, Gabriel Reygondeau^1^, U. Rashid Sumaila^1^, Alessandro Tagliabue^5^, Colette C.C. Wabnitz^1,6^, and William W.L. Cheung^1^"
output: 
  bookdown::pdf_document2:
    number_section: no
    toc: no
    latex_engine: xelatex
reference_docx:  ../References/sci_template.docx
bibliography: ../References/ToE_Ref.bib
csl: ../References/gcb.csl
header-includes:
  - \usepackage{setspace}
  - \usepackage{caption}
  - \usepackage[left]{lineno} # for numbers in lines
  - \usepackage{float} # Use the 'float' package
  - \captionsetup[figure]{name = Fig}
  - \floatplacement{figure}{H}
---

>>>>

---
title: "Timing and magnitude of climate driven range shifts in transboundary fish stocks challenge their management"
date: "Affiliations: ^1^Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada.^2^Center for Limnology, University of Wisconsin, Madison. ^3^Climate and Environmental Physics, Physics Institute, University of Bern. ^4^Oeschger Centre for Climate Change Research, University of Bern, Switzerland. ^5^School of Environmental Sciences, University of Liverpool. ^6^Stanford Center for Ocean Solutions, Stanford University, Stanford, United States"
subtitle: "Juliano Palacios-Abrantes*^1,2^, Thomas L. Frölicher^3,4^, Gabriel Reygondeau^1^, U. Rashid Sumaila^1^, Alessandro Tagliabue^5^, Colette C.C. Wabnitz^1,6^, and William W.L. Cheung^1^"
output: 
  bookdown::word_document2:
    number_section: no
    toc: no
    latex_engine: xelatex
always_allow_html: true
reference_docx:  ../References/sci_template.docx
bibliography: ../References/ToE_Ref.bib
csl: ../References/gcb.csl
header-includes:
  - \usepackage{setspace}
  - \usepackage{caption}
  - \usepackage[left]{lineno} # for numbers in lines
  - \usepackage{float} # Use the 'float' package
  - \captionsetup[figure]{name = Fig}
  - \floatplacement{figure}{H}
---
